Maps between Categories -- Functors

### 2017-07-28 notes/notes-2/notes-2.tex
Fixed some obvious bugs.

\begin{document}
\title{Presheaves, Representables and\\the Yoneda Lemma}
\author{Dominik Wagner, Felix Rech}
\maketitle

We want to define structure-preserving maps between categories.
Since the morphisms are are most interesting part of a category, such a map should not just operate on objects, but on morphisms to.
In order to preserve the structure, it has to map identity morphisms to identity morphisms and compositions of morphisms to compositions.
This is made precise in the following definition.

@@

In the next few examples we will talk about a vary simple type of algebraic structures with a binary operation that we now define.

@@

This is the same as the definition of \emph{groups} except that we don't require inverses.
Similar to homomorphisms on groups, we define homomorphisms on monoids.

@@

Note that this definition only speaks about what heapens to morphisms between the \emph{same pair} of objects.
For morphisms $A \xrightarrow{f, g} B$, we can conclude that $F(A) = F(B)$ implies $A = B$ but for a morphism $A \xrightarrow{f} B$ and a morphism $C \xrightarrow{g} D$ between another pair of objects, the faithfulness of $F$ doesn't tell us anything.
Let us consider a functor like in the following graphic as an example.
\[ \begin{tikzpicture}
    \draw (0, 0) rectangle (2, 3);
    \node (A) at (0.5, 2.5) {$A$};
    \node (C) at (1, 0.5) {$C$};
    \node (B) at (1.5, 2.5) {$B$};
    \draw[->] (A) to node[auto, swap] {$f$} (C);
    \draw[->] (B) to node[auto] {$g$} (C);

>>>>

\begin{document}
\title{Maps between Categories -- Functors}
\author{Felix Rech \and Dominik Wagner}
\maketitle

We want to define structure-preserving maps between categories.
Since the morphisms are most interesting part of a category, such a map should not just operate on objects, but on morphisms, too.
In order to preserve the structure, it has to map identity morphisms to identity morphisms and compositions of morphisms to compositions.
This is made precise in the following definition.

@@

In the next few examples we will talk about a very simple type of algebraic structure with a binary operation that we now define.

@@

This is the same as the definition of \emph{groups} except that we do not require inverses.
Similar to homomorphisms on groups, we define homomorphisms on monoids.

@@

Note that this definition only speaks about what happens to morphisms between the \emph{same pair} of objects.
For morphisms $A \xrightarrow{f, g} B$, we can conclude that $F(A) = F(B)$ implies $A = B$ but for a morphism $A \xrightarrow{f} B$ and a morphism $C \xrightarrow{g} D$ between another pair of objects, the faithfulness of $F$ does not tell us anything.
Let us consider a functor like in the following graphic as an example.
\[ \begin{tikzpicture}
    \draw (0, 0) rectangle (2, 3);
    \node (A) at (0.5, 2.5) {$A$};
    \node (C) at (1, 0.5) {$C$};
    \node (B) at (1.5, 2.5) {$B$};
    \draw[->] (A) to node[auto, swap] {$f$} (C);
    \draw[->] (B) to node[auto] {$g$} (C);
